Greenhouse gas emissions model - making scenarios

### 2021-11-12 Scenarios_report.Rmd
model fixed

```{r}
knitr::kable(read.table("data/scenarios.csv", sep = ","))

@@

```{r}
scenarios<-read.table("data/scenarios.csv", sep = ",", fileEncoding = "UTF-8-BOM",header=TRUE)

Kenyaherds<-read.table("data/Kenya_baseline_individual_cow_wNotes.csv", sep = ",",
                       fileEncoding = "UTF-8-BOM", header=TRUE)

>>>>

```{r}
knitr::kable(read.table("data/scenarios.csv", sep = ",", fileEncoding = "UTF-8-BOM",header=TRUE))

@@

```{r}
Kenyaherds<-read.table("data/Kenya_baseline_individual_cow_wNotes.csv", sep = ",",
                       fileEncoding = "UTF-8-BOM", header=TRUE)
